### 2014-10-09 Pero_Transcriptome.tex
adding Dryad links

Transcriptome assemblies for each tissue type were accomplished using the program Trinity \citep{Haas:2013jq}. The raw assemblies for brain, liver, testes, and kidney contained 185425, 222096, 180233, and 514091 assembled sequences respectively. This assembly was filtered using a blastN procedure against the \textit{Mus} cDNA and ncRNA and \textit{P. maniculatus} cDNAs, which resulted in a final dataset containing 68331 brain-derived transcripts, 71041 liver-derived transcripts, 67340 testes-derived transcripts, and 113050 kidney-derived transcripts. Mapping the error-corrected adapter/quality trimmed reads to these datasets resulted in mapping 94.98\% (87.01\% properly paired) of the brain-derived reads to the brain transcriptome, 96.07\% (88.13\% properly paired) of the liver-derived reads to the liver transcriptome, 96.81\% (85.10\% properly paired) of the testes-derived reads to the testes transcriptome, and 91.87\% (83.77\% properly paired) of the kidney-derived reads to the kidney transcriptome. Together, these statistics suggest that the tissue-specific transcriptomes are of extremely high quality. All tissue-specific assemblies are to be made available on Dryad, and until then are stored on Dropbox (\url{https://www.dropbox.com/sh/2jwzd8p6n6eluco/AAAO3nSdXb_u4wtQZRTwqW9ia?dl=0}). \\

@@

We then estimated gene expression on each of these tissue-specific datasets, which allowed us to understand expression patterns in the multiple tissues (Pero.tissue.xprs, will be made available on Dryad, until then on Dropbox (\url{https://www.dropbox.com/sh/2jwzd8p6n6eluco/AAAO3nSdXb_u4wtQZRTwqW9ia?dl=0})). Specifically, we constructed a Venn diagram ({\hypertarget{Figure 1}{Figure 1}}) that allowed us to visualize the proportion of genes whose expression was limited to a single tissue and those whose expression was ubiquitous. 66324 transcripts are expressed in all tissue types, while 13086 are uniquely expressed in the kidney, 2222 in the testes, 3580 in the brain, and 2798 in the liver. The kidney appears to an outlier in the number of unique sequences, though this could be the result of the recovery of more lowly expressed transcripts or isoforms.  \\

@@

After expression estimation, the filtered assemblies were concatenated together, and after the removal of redundancy with cd-hit-est, 122,584 putative transcripts remained (to be made available on Genbank, and until then are stored on Dropbox \url{https://www.dropbox.com/sh/2jwzd8p6n6eluco/AAAO3nSdXb_u4wtQZRTwqW9ia?dl=0}.). From this filtered concatenated dataset, we extracted 71626 putative coding sequences (72Mb, to be made available on Dryad). Of these 71626 sequences, 38221 contained complete open reading frames (containing both start and stop codons), while the others were either truncated at the 5-prime end (20239 sequences), the 3-prime end (6445 sequences), or were internal (6721 sequencing with neither stop nor start codon). The results of a Pfam search conducted on the predicted amino acid sequences will be found on Dryad, and until then are stored on Dropbox \url{https://www.dropbox.com/sh/2jwzd8p6n6eluco/AAAO3nSdXb_u4wtQZRTwqW9ia?dl=0}.. \\

>>>>

Transcriptome assemblies for each tissue type were accomplished using the program Trinity \citep{Haas:2013jq}. The raw assemblies for brain, liver, testes, and kidney contained 185425, 222096, 180233, and 514091 assembled sequences respectively. This assembly was filtered using a blastN procedure against the \textit{Mus} cDNA and ncRNA and \textit{P. maniculatus} cDNAs, which resulted in a final dataset containing 68331 brain-derived transcripts, 71041 liver-derived transcripts, 67340 testes-derived transcripts, and 113050 kidney-derived transcripts. Mapping the error-corrected adapter/quality trimmed reads to these datasets resulted in mapping 94.98\% (87.01\% properly paired) of the brain-derived reads to the brain transcriptome, 96.07\% (88.13\% properly paired) of the liver-derived reads to the liver transcriptome, 96.81\% (85.10\% properly paired) of the testes-derived reads to the testes transcriptome, and 91.87\% (83.77\% properly paired) of the kidney-derived reads to the kidney transcriptome. Together, these statistics suggest that the tissue-specific transcriptomes are of extremely high quality. All tissue-specific assemblies are available on Dryad (\url{http://dx.doi.org/10.5061/dryad.qf1dp}). \\

@@

We then estimated gene expression on each of these tissue-specific datasets, which allowed us to understand expression patterns in the multiple tissues (Pero.tissue.xprs, available on Dryad (\url{http://dx.doi.org/10.5061/dryad.qf1dp})). Specifically, we constructed a Venn diagram ({\hypertarget{Figure 1}{Figure 1}}) that allowed us to visualize the proportion of genes whose expression was limited to a single tissue and those whose expression was ubiquitous. 66324 transcripts are expressed in all tissue types, while 13086 are uniquely expressed in the kidney, 2222 in the testes, 3580 in the brain, and 2798 in the liver. The kidney appears to an outlier in the number of unique sequences, though this could be the result of the recovery of more lowly expressed transcripts or isoforms.  \\

@@

After expression estimation, the filtered assemblies were concatenated together, and after the removal of redundancy with cd-hit-est, 122,584 putative transcripts remained (Pero.BLTK.fasta - available on Dryad: \url{http://dx.doi.org/10.5061/dryad.qf1dp}.). From this filtered concatenated dataset, we extracted 71626 putative coding sequences (72Mb, available on Dryad). Of these 71626 sequences, 38221 contained complete open reading frames (containing both start and stop codons), while the others were either truncated at the 5-prime end (20239 sequences), the 3-prime end (6445 sequences), or were internal (6721 sequencing with neither stop nor start codon). The results of a Pfam search conducted on the predicted amino acid sequences are on Dryad (\url{http://dx.doi.org/10.5061/dryad.qf1dp}). \\
